Paper Figures and Text

### 2024-03-19 Fish Data Analysis/Paper_Figures.qmd
Single Fish example made

text_size = 16
```

@@

>>>>

text_size = 16

# for turning data
x_offset <- 1.95
y_offset <- 1.15
```

@@

Single Fish Figure

single_comp_data <- read.csv("Data/Fish_Comp_Values_3D_Single.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "S", "Single", "Jingle")) %>%
                           mutate(Darkness = ifelse(Darkness == "S", "Single", "Jingle")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("Single"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Single"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
                           mutate(Type = "Single")

top_edge <- ceiling(max(single_comp_data$Fish1_Y)) - y_offset 
bottom_edge <- floor(min(single_comp_data$Fish1_Y)) + y_offset
left_edge <- floor(min(single_comp_data$Fish1_X)) + x_offset
right_edge <- ceiling(max(single_comp_data$Fish1_X)) - x_offset

single_fish_mean_angles_middle <- single_comp_data %>% filter(Fish1_X >= left_edge & Fish1_X <= right_edge) %>%
                                                filter(Fish1_Y >= bottom_edge & Fish1_Y <= top_edge) %>%
                                                 #normalize
                                                 mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS, na.rm = T))

#Combine -75 to -105 with 75 to 105
single_perp_angle_df_middle <- single_fish_mean_angles_middle %>% filter(Angle >= deg2rad(75) & Angle <= deg2rad(105))
single_perp_angle_df_neg_middle <- single_fish_mean_angles_middle %>% filter(Angle >= deg2rad(-105) & Angle <= deg2rad(-75)) %>%
                                                                 mutate(Fish1_Yaw_Heading_PS = -1*Fish1_Yaw_Heading_PS)
single_perp_angle_df_middle <- rbind(single_perp_angle_df_middle,single_perp_angle_df_neg_middle) %>% mutate(Label = "Edges Removed")

single_fish_mean_angles_all <- single_comp_data %>% mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS, na.rm = T))

single_perp_angle_df_all <- single_fish_mean_angles_all %>% filter(Angle >= deg2rad(75) & Angle <= deg2rad(105))
single_perp_angle_df_neg_all <- single_fish_mean_angles_all %>% filter(Angle >= deg2rad(-105) & Angle <= deg2rad(-75)) %>%
                                                                mutate(Fish1_Yaw_Heading_PS = -1*Fish1_Yaw_Heading_PS)
single_perp_angle_df_all <- rbind(single_perp_angle_df_all,single_perp_angle_df_neg_all) %>% mutate(Label = "All Data")

single_perp_angle_graphing <- rbind(single_perp_angle_df_middle,single_perp_angle_df_all)

t.test(single_perp_angle_df_middle$Fish1_Yaw_Heading_PS)

single_plot <- ggplot(single_perp_angle_graphing, aes(x = Fish1_Yaw_Heading_PS, fill = Label))+
  geom_histogram(aes(y=0.5*..density..),binwidth=1,position='identity', alpha = 0.5)+
  theme_classic()+
  scale_fill_manual(values = c("#CE2414","#138EC2"))+
  ylab("Proportion of Values")+
  xlab("Turning Angle (Degrees / s)")+
  xlim(-5,5)

single_plot

ggsave("Paper Figures/Edge_Removal_Single_Fish.png", single_plot, width = 7, height = 7)
